---
title: "Lab10"
author: "Soyeon Lee"
date: "11/26/2020"
output: html_document
---
Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.
Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867.

Note, the paper, the data, and an existing reproducible analysis of this data is available at https://crumplab.github.io/statisticsLab/lab-10-factorial-anova.html#important-stuff-4

The re-analysis should focus only on Experiment 3. There are three main goals

1. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)
2. Reproduce a graph of the means, like shown in the paper (2 points)
3. Present a power-curve analysis for the design. (2 points)

```{r}
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyverse)

#load data and change the weird column name 
all_data<-read.csv("open_data/stroop_stand.csv")
all_data<-all_data%>% rename(congruent_stand=ï..congruent_stand)
```

```{r}
#Stand Stroop effect using paired sample t test
(stand_stroop<-t.test(all_data$congruent_stand,
                      all_data$incongruent_stand,
                      paired=TRUE))

#sit Stroop effect using paired sample t test
(sit_stroop<-t.test(all_data$incongruent_sit,
                   all_data$congruent_sit,
                   paired=TRUE))
```
The stroop effects in both the sitting condition, M=118.9 ms, t(49)=16.52, p<.01, d=2.376, and the standing condition, M=95.9 ms, t(49)=14.327, p<.01, d=2.304, were highly reliable,...
    Our reproduction analysis shows:
The stroop effects in both the sitting condition,`r papaja::apa_print(sit_stroop)$full_result`, and the standing condition, `r papaja::apa_print(stand_stroop)$full_result`, were highly reliable,...