---
title: "Lab10"
author: "Soyeon Lee"
date: "11/26/2020"
output: html_document
---
Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.
Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867.

Note, the paper, the data, and an existing reproducible analysis of this data is available at https://crumplab.github.io/statisticsLab/lab-10-factorial-anova.html#important-stuff-4

The re-analysis should focus only on Experiment 3. There are three main goals

1. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)
2. Reproduce a graph of the means, like shown in the paper (2 points)
3. Present a power-curve analysis for the design. (2 points)

```{r}
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyverse)

#load data and change the weird column name 
all_data<-read.csv("open_data/stroop_stand.csv")
all_data<-all_data%>% rename(congruent_stand=ï..congruent_stand)
```

```{r}
##Part 1: Reproduce the analysis (Confidence 40) 

#Stand Stroop effect using paired sample t test
(stand_stroop<-t.test(all_data$incongruent_stand,
                      all_data$congruent_stand,
                      paired=TRUE))

#sit Stroop effect using paired sample t test
(sit_stroop<-t.test(all_data$incongruent_sit,
                   all_data$congruent_sit,
                   paired=TRUE))

(stroop_mean_difference<-sit_stroop$estimate - stand_stroop$estimate)
```
The authors wrote:
The Stroop effects in both the sitting condition, M=118.9 ms, t(49)=16.52, p<.01, d=2.376, and the standing condition, M=95.9 ms, t(49)=14.327, p<.01, d=2.304, were highly reliable,...

Our reproduction analysis:
The Stroop effects in both the sitting condition,`r papaja::apa_print(sit_stroop)$full_result`, and the standing condition, `r papaja::apa_print(stand_stroop)$full_result`, were highly reliable,...

```{r}
#Get difference RT for each subject and store them as stand or sit_stroop scores
stand_stroop_scores<-all_data$incongruent_stand - 
                     all_data$congruent_stand
sit_stroop_scores<-all_data$incongruent_sit -
                   all_data$congruent_sit

#stroop difference scores using a single sample test
#a single sample test for interaction of the Stroop effect and sit/stand
stroop_differences<-sit_stroop_scores - stand_stroop_scores

(interaction_results<-t.test(stroop_differences))

#Stroop effect comparison between sitting and standing using the paired sample t test
(paired_results<-t.test(stand_stroop_scores,
                        sit_stroop_scores,
                        paired=TRUE))
```
The authors wrote:
...but the most significant finding again was the shrinkage of the effect when participants were standing, F(1,49)=8.964, p=.004, np2=.155.

Our reproduction analysis: 
We found that the same result using a one-sample t test, `r apa_print(interaction_results)$full_result`.

We found the same mean difference `r apa_print(interaction_results)$estimate` and that we found the same p-value (.004).
```{r}
##Part 2: Plotting (Confidence 0)
library(tidyr)

#convert current table into a long form 3 col table
stroop_df<-all_data%>%
              pivot_longer(cols=1:4,
                           names_to=c("Congruency", "Posture"),
                           names_sep="_",
                           values_to="RTs")

#get means and SE for each posture-congruency condition 
overall_means<-stroop_df%>%
                  group_by(Posture,Congruency)%>%
                  summarise(meanRT=mean(RTs),
                            SEMRT=(sd(RTs)/sqrt(length(RTs)))) 

#Plot
ggplot(overall_means,aes(x=Posture,
                         y=meanRT,
                         group=Congruency,
                         fill=Congruency))+
  geom_bar(stat="identity", position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT+SEMRT),
                    position=position_dodge(width=0.9),
                    width=0.2,
                    color="black")+
  coord_cartesian(ylim=c(500,1000))
```

```{r}
##Part 3: Power curve (Confidence 50)
effect_sizes <- seq(0,1.5,.1)
prop_significant <-c()

for(i in 1:length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50,rnorm(1, effect_sizes[i], 1)),
                                   mu=0) $p.value)

  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
}

plot_df <- data.frame(effect_sizes,
                      prop_significant)

ggplot(plot_df, aes(x=effect_sizes,y=prop_significant))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks=seq(0,1,.1)) +
  ylab("Proportion Significant")



```

