---
title: "Lab5"
author: "Soyeon Lee"
date: "10/8/2020"
output: html_document
---

1. Trust but verify. We trust that the rnorm() will generate random deviates in accordance with the definition of the normal distribution. For example, we learned in this lab, that a normal distribution with mean = 0, and sd =1 , should only produce values larger than 2.5 with a specific small probability, that is P(x>2.5) = 0.006209665. Verify this is approximately the case by randomly sampling 1 million numbers from this distribution, and calculate what proportion of numbers are larger than 2.5. (1 point)
Confidence:80
```{r}
#get proportion greater than 2.5
#verify this using a sampling distribution
pnorm(q=2.5, mean=0,sd=1,lower.tail=FALSE)

my_sample<-rnorm(1000000,mean=0,sd=1)
selection<-my_sample[my_sample>2.5]
length(selection)/1000000
```

2. If performance on a standardized test was known to follow a normal distribution with mean 100 and standard deviation 10, and 10,000 people took the test, how many people would be expected to achieve a score higher than 3 standard deviations from the mean? (1 point)
Confidence:90
```{r}
#10000 multiplied by the proportion of getting a value greater than 3 deviations
10000*pnorm(q=130, mean=100, sd=10, lower.tail=FALSE)

#round up to a whole number: 14 people
```
3. You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger.

Create a sampling distribution of the mean for this scenario with at least 10,000 sample means (1 point). Then, calculate the proportion of sample means that are 12 or larger (1 point).
Confidence:90
```{r}
#get 10000samples of sample size=25 from a normal distribution with mean=10 and standard deviation=20
#plot histogram

my_sampleMeans<-replicate(10000,mean(rnorm(n=25, mean=10, sd=20)))
hist(my_sampleMeans)

#the proportion of sample means greater than or equal to 12
length(my_sampleMeans[my_sampleMeans>=12])/length(my_sampleMeans)
```
 
4. You randomly sample 100 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger.

Create a sampling distribution of the mean for this scenario with at least 10,000 sample means. Then, calculate the proportion of sample means that are 12 or larger. Is the proportion different from question 3, why? (1 point)
Confidence:90
```{r}
#get 10000 samples of sample size=100 from a normal distribution with mean=10 and standard deviation=20
#plot histogram

my_sampleMeans<-replicate(10000,mean(rnorm(n=100, mean=10, sd=20)))
hist(my_sampleMeans)

#the proportion of sample means greater than or equal to 12
length(my_sampleMeans[my_sampleMeans>=12])/length(my_sampleMeans)

#The proportion in #4 is smaller because scores vary less with a larger sample size in #4.  Compared to distribution #3, more scores are concentrated around the mean in #4 distribution. This makes the sample mean of 12 less common, reflected in the smaller value of proportion for #4.
```

5. You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample standard deviation of 15. You want to know the probability that you could have received a sample standard deviation of 15 or less.

Create a sampling distribution of standard deviations for this scenario with at least 10,000 sample standard deviations. Then, calculate the proportion of sample standard deviations that are 15 or less. (1 point)
```{r}
#get 10000 samples of sample size=25 from a normal distribution with mean=10 and standard deviation=20
#plot histogram

sampling_distribution<-replicate(10000,sd(rnorm(25,10,20)))
hist(sampling_distribution)

#the proportion of sample standard deviation greater than or equal to 15
length(sampling_distribution[sampling_distribution<=15])/10000
```

