---
title: "Lab7"
author: "Soyeon Lee"
date: "10/22/2020"
output: html_document
---

1. A test-taker answered 50 true/false questions and received a score of 60% correct. Report the results of a binomial test and explain whether you think the test-score could be produced by the test-taker randomly guessing on each question. (2 points)
Confidence: 80
```{r}
test_result<-binom.test(x=30, 
           n=50, 
           p=.5, 
           alternative="greater")

#The probability of getting 60% or more of the questions correct is .1013.  This probability is lower than random chance but not rare.  Thus, we cannot reject that the test-taker did not randomly guess each question. Increasing the number of trials would lower the probability and increase the likelihood that the test result is a product of guesses. 
```

2. An examiner wants to make a TRUE/FALSE test, but is still deciding how many questions they will include. They want to make sure that it would be very difficult to simply randomly guess and be able to score any higher than 55% percent. How many questions would the examiner need to use to be confident that scores of 55% or higher were not produced by chance? (2 points)
Confidence:100
```{r}
binom.test(x=330,
           n=600,
           p=.5,
           alternative="greater")

#With 600 questions (trials), the p-value is less than .01. Students will be unlikely to score 55% or higher by guessing each question. 
```

3. A test has 5 TRUE/FALSE questions (each with one right answer) and 5 multiple choice questions with four choices each (each with only one right answer).

create a sampling distribution or probability distribution to illustrate how a random chance process could perform on this test. (1 point)

What is the probability that randomly guessing on each question could allow a person to receive 75% or greater on this test? (1 point)
Confidence:10
```{r}
simulated_test <- replicate(10000, rbinom(n= rep(1,10), size=1, prob= c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25)))

#probability distribution of the simulated test means
simulated_scores<-colSums(simulated_test)/10

library(ggplot2)

qplot(simulated_scores)+
  geom_histogram()

#probability of producing 75% or greater on this test by guessing 
length(simulated_scores[simulated_scores>=.75])/length(simulated_scores)

```

