---
title: "Lab8"
author: "Soyeon Lee"
date: "10/30/2020"
output: html_document
---

1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of z-scores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.
-Advanced: Have an option so that the function will convert the raw scores to z-scores in one of two ways:
-using user provided mean and standard deviation
-using the calculated mean and standard deviation from the raw scores
Confidence:90
```{r}
#first option
to_zscores_A<-function(raw,mu,st_dev){
  zscores<-(raw-mu)/st_dev
  return(zscores)
}

a<-c(1,2,4,5,6)
to_zscores_A(a,2,1)
```
```{r}
#second option
to_zscores_B<-function(raw){
  zscores<-(raw-mean(raw))/sd(raw)
  return(zscores)
}

to_zscores_B(a)
```

2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).

-Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).
Confidence:10

```{r}
#the ztest function returns the probability larger than the input sample_mean
ztest<-function(sample_mean, sample_size, mu, sigma){
  sampl_distr_mean<-mu
  sampl_distr_sd<-sigma/sqrt(sample_size)
  
  p_value<-pnorm(sample_mean,
                 sampl_distr_mean,
                 sampl_distr_sd,
                 lower.tail=FALSE)
  return(p_value)
}

ztest(sample_mean=50, sample_size =25, mu=40, sigma=7)
```
```{r}
#this function returns the probability value for a one-or two-tailed test

ztest<-function(sample_mean, sample_size, mu, sigma, two_tailed=TRUE){
  sampl_distr_mean <-mu
  sampl_distr_sd <-sigma/sqrt(sample_size)
  
  abs_difference<- abs(sample_mean-mu)
  
  p_value<- pnorm((mu+abs_difference),
                  sampl_distr_mean,
                  sampl_distr_sd,
                  lower.tail = FALSE)
  
  if(two_tailed==TRUE) p_value<- p_value*2
  return(p_value)
}

#demonstrate the function
ztest(sample_mean=50,
      sample_size=25,
      mu=40,
      sigma=7,
      two_tailed=FALSE)
```
```{r}
# The result indicates that the probability of obtaining a sample mean of 50 or greater is 4.570531e-13.  When we assume that infinite samples of 25 scores were taken from the specified normal distribution, the probability of their mean being 50 is not too common but still probable. 
```




