---
title: "Lab9"
author: "Soyeon Lee"
date: "11/11/2020"
output: html_document
---

1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).
Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).
```{r}
#make the data legible in a table format
#used csv delimited because I don't have the normal csv option available

the_data<-read.csv(file="lab 9 data/infant_choice_data.csv")

#extract only the experiment 1 data
library(dplyr)
e1_data<- the_data%>% filter(ExperimentNumber==1)

#conduct binomial test
#p=0.26

sum_C <- sum(e1_data$Infant.Chose.C)
total_C<- length(e1_data$Infant.Chose.C)

binomial_p<-pbinom(q=total_C-sum_C,
                   size=total_C,
                   prob=.5,
                   lower.tail=TRUE)*2

#second way?
block_c <- binom.test(sum_C, total_C, p=.5, alternative="two.sided")
```


```{r}
#chi-square for gender
#df=1, n=21, chi sq value is 0.15, p=.696

library(tidyr)

#create a 2 by 2 table
gender_choice_table<-e1_data%>%
  group_by(Gender, Infant.Chose.C)%>%
  summarize(counts=n())%>%
  pivot_wider(names_from=c(Gender),
              values_from=counts)

gender_choice_table<-gender_choice_table[,2:3]

#get expected values by attempting a chi square test using the function
#get chi square via a long method because there are values less than 5

gender_Xsq<-chisq.test(gender_choice_table)

uncorrected_Xsq<-
  sum((gender_Xsq$observed-gender_Xsq$expected)^2/gender_Xsq$expected)

#get p-value 
gender_Xsq_unc<-pchisq(q=uncorrected_Xsq, df=1, lower.tail=FALSE)

#verify answers
uncorrected_Xsq
gender_Xsq_unc
```
```{r}
#chi-square for age 
#df=19, n=21, chi sq value is 18.24, p=.506

#create a table 
age_table<-e1_data%>%
  group_by(AgeMonths, Infant.Chose.C)%>%
  summarize(counts=n())%>%
  pivot_wider(names_from=c(AgeMonths),
              values_from=counts)

#convert na to 0, and the table into a matrix
age_table[is.na(age_table)]<- 0
age_table<-as.matrix(age_table[,2:21])

#get chi square 
age_xs<-chisq.test(age_table)

#verify results 
age_xs
```
```{r}
#report re-analysis 
```

